---
title: "r4ds_wrangle_exercises_10-11"
author: "Brandon Cox"
date: "9/25/2017"
output: 
  github_document:
    toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
```

## Wrangle: Tibbles

### 10.5 Exercises


1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).

A tibble will show you the data types and the first 15 rows.

```{r}
class(mtcars)
print(mtcars)
print(as_tibble(mtcars))
```

2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

You have to be more explicit with a tibble, which in turn give more reliability. Data frames can give unexpected results because it will give a result back if you partially match a column.

3. If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

```{r}
tibbleCar <- as_tibble(mtcars)
var <- "mpg"
tibbleCar[var]
```

4. Practice referring to non-syntactic names in the following data frame by:
    1. Extracting the variable called 1
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
annoying$`1`
annoying[1]
```
    2. Plotting a scatterplot of 1 vs 2
```{r}
ggplot(annoying, aes(`1`, `2`)) +
  geom_point()
```
    3. Creating a new column called 3 which is 2 divided by 1
```{r}
annoying <- mutate(annoying, `3` = `2` / `1`)
print(annoying)
```
    4. Renaming the columns to one, two and three
```{r}
annoying <- rename(annoying, 
                   one = `1`,
                   two = `2`,
                   three = `3`)
print(annoying)
```
5. What does tibble::enframe() do? When might you use it?
```{r}
help("enframe")
# enframe() converts named atomic vectors or lists to two-column data frames. For unnamed vectors, the natural sequence is used as name column.
enframe(c(a = 1, b = 2))
```
    
6. What option controls how many additional column names are printed at the footer of a tibble?
```{r}
?`tibble-package`
#tibble.max_extra_cols - Number of extra columns printed in reduced form. Default: 100.
```


## Wrangle: Data Import

### 11.2.2 Exercises

1. What function would you use to read a file where fields were separated with
“|”?
```
read_delim(file, delim = "|")
```
1. Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?
    
    file, col_names, cal_types, locale, na, quoted_na, comment, trim_ws
    skip, n_max, guess_max, progress

1. What are the most important arguments to read_fwf()?
    
    col_positions - because every field is in the same place in every line.
    
1. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?

```{r}
delimTest <- "x,y\n1,'a,b'"
read_delim(delimTest, delim = ",", quote = "'")
```

1. Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

```{r}
#read_csv("a,b\n1,2,3\n4,5,6") - add c
read_csv("a,b,c\n1,2,3\n4,5,6")
#read_csv("a,b,c\n1,2\n1,2,3,4") - add value to c on row 1 and remove from row 2
read_csv("a,b,c\n1,2,3\n1,2,3")
#read_csv("a,b\n\"1") - no idea what is trying to be done here
#read_csv("a,b\n1,2\na,b") - everthing looks okay here?
read_csv("a,b\n1,2\na,b")
#read_csv("a;b\n1;3") - use read_csv2
read_csv2("a;b\n1;3")
```

### 11.3.5 Exercises

1. What are the most important arguments to locale()?
    
    date_names, date_format, time_format, decimal_mark, grouping_mark, tz
    
1. What happens if you try and set decimal_mark and grouping_mark to the same character? What happens to the default value of grouping_mark when you set decimal_mark to “,”? What happens to the default value of decimal_mark when you set the grouping_mark to “.”?

    You get an error stating that they must be different.
 
1. I didn’t discuss the date_format and time_format options to locale(). What do they do? Construct an example that shows when they might be useful.

    They let you create default formats for your locale.

1. If you live outside the US, create a new locale object that encapsulates the settings for the types of file you read most commonly.
    
    YAYA


1. What’s the difference between read_csv() and read_csv2()?
    
    The delimiter for ```read_csv2``` is a ```;```. Some places use commas instead of decimmals so it helps with that.


1. What are the most common encodings used in Europe? What are the most common encodings used in Asia? Do some googling to find out.
    
    Europe - uses subset of ISO 8859. Asia - uses various different ones depending on the language/country. https://en.wikipedia.org/wiki/Character_encoding

1. Generate the correct format string to parse each of the following dates and times:

```{r}
d1 <- "January 1, 2010"
parse_date(d1, "%B %d, %Y")

d2 <- "2015-Mar-07"
parse_date(d2, "%Y-%b-%d")

d3 <- "06-Jun-2017"
parse_date(d3, "%d-%b-%Y")

d4 <- c("August 19 (2015)", "July 1 (2015)")
parse_date(d4, "%B %d (%Y)")

d5 <- "12/30/14" # Dec 30, 2014
parse_date(d5, "%D")

t1 <- "1705"
parse_time(t1, "%H%M")

t2 <- "11:15:10.12 PM"
parse_time(t2, "%I:%M:%OS %p")
```
